%!TEX TS-program = xelatex
\documentclass[print]{friggeri-cv}

\begin{document}
\header{Kristijan}{Perusko}
       {software engineer}


% In the aside, each new line forces a line break
\begin{aside}
  \section{About}
    Jamaica Estates
    NY 11432
~
    \href{mailto:kristijan.perusko@yahoo.com}{kristijan.perusko@yahoo.com}
    111.111.111
  \section{Links}  
    Linkedin://  \href{https://www.linkedin.com/in/kperusko}{kperusko}
    Bitbucket:// \href{https://bitbucket.org/kperusko}{kperusko}    
    Github:// \href{https://github.com/kperuska}{kperusko}
    StackOverflow:// \href{http://stackoverflow.com/users/515053/christian-p}{christian-p}
  \section{Languages}
    English, Croatian
  \section{Programming}
    {\color{red} $\varheartsuit$} Scala
    PHP, JavaScript
    CSS \& HTML
~     
    \emph{Some experience:}
    Python, Java
    C\# (Silverlight), VB.Net
    Racket, Octave
  \section{Db}
    MongoDB, MySQL
  \section{Os}
    {\color{red} $\varheartsuit$} Linux 
    Ubuntu, Debian 
    Fedora, CentOS
    Windows
  \section{Other}
    Apache2, Nginx
    RabbitMQ
    AWS, Heroku, S3
    Mercurial, Git, SVN
\end{aside}

\section{Summary}

I'm interested in functional programming, distributed systems, databases, machine learning and game programming. I can work as a full stack or back-end SE. I'm passionate about learning and I love solving hard problems. 

\section{Experience}

\begin{entrylist}
  \entry
    {since 2008}
    {Novatec}
    {Team lead | Software engineer}
    {Worked on in-house projects for two years as a software engineer. Became a team lead to build a booking system and more than 15 customer facing sites. Had several roles including project/team lead, administration and configuration of MongoDB and MySQL DBs, provisioning of Debian servers.}
  \entry
    {2007-2008}
    {Tempo}
    {IT administrator}
    {Principal responsibility in several areas including Windows administration and user support, configuration and management of infrastructure and equipment in 8 remote offices. Managed system upgrade for compliance with EU customs legislation.}
  \entry
    {2005-2007}
    {Vlado elektronika}
    {Sofware and electrical QA engineer}
    {Created hardware testbed and software for computer aided testing of intrusion alarm system. This system automated 90\% of the tests and lowered the testing time for each board by 60\%.}
\end{entrylist}

\section{Education}

\begin{entrylist}
  \entry
    {since 2013}
    {BS of information tehnology}
    {Veleuciliste u Rijeci}
    {\emph{Silverlight 5 and MS Sync Framework}}
  \entry
    {since 2002}
    {Electrical engineering}
    {Mate Blazina high school}
    {\emph{DC servo driver controlled by IR remote}}
\end{entrylist}
\section{Certifications}
\begin{entrylist}
  \entry
    {07 2014} 
    {M202: MongoDB Advanced Deployment and Operations}
    {MongoDB}
    {\emph{MongoDB}}
%  \entry
%    {01 2014}
%    {Control of Mobile Robots}
%    {Coursera}
%    {\emph{Georgia Institute of tehnology}}
  \entry
    {11 2013}
    {Principles of Reactive Programming}
    {Coursera}
    {\emph{École Polytechnique Fédérale de Lausanne}}
  \entry
    {10 2013}
    {Machine Learning} 
    {Coursera}
    {\emph{Stanford University}}
  \entry
    {10 2013}
    {Interactive Programming in Python}
    {Coursera}
    {\emph{Rice University}}
  \entry
    {10 2013}
    {M101JS MongoDB for Node.js Developers}
    {MongoDB}
    {\emph{MongoDB}}
  \entry
    {09 2013}
    {Functional Programming Principles in Scala}
    {Coursera}
    {\emph{Ecole Polytechnique Federale de Lausanne}}
%  \entry
%    {09 2013}
%    {Introduction to Systematic Program}
%    {Coursera}
%    {\emph{The University of British Columbia}}
  \entry
    {06 2013}
    {Startup Engineering}
    {Coursera}
    {\emph{Stanford University}}
\end{entrylist}
\end{document}
